\tool

### 2018-02-09 paper/paper.tex
Related work paper updates

%Researchers have explored methods for increasing tool discovery among software users. Fischer suggests that some of the more popular methods for raising tool awareness, such as documentation and help menus, are ineffective for increasing adoption of useful tools and features~\cite{ActiveHelpSystems}. These \textit{passive help systems} require users to first recognize the system's existence, navigate to the items, and then manually search for help. However, users rarely seek help by discovering new functionality and will often just rely on their own previous knowledge~\cite{something}. 
%
%Active help systems are the preferred method of helping users discover new functionality in software. These systems automatically recommend useful tools to software users. However, there remains room for improvement among these system-to-user recommendation systems. For example, Clippy, an intelligent office assistant for Microsoft Office products, was able to automatically suggest tools and features to Microsoft software users. However, the system was found ineffective and eventually removed. Peer interactions and receptiveness are effective~\cite{vlhcc17}... Previous research has shown that user-to-user recommendations are the most effective mode of increasing awareness of tools among software users~\cite{MurphyHill2011PeerInteraction}

@@

Our approach is based on previous research examining how users learn about and discover tools, the lack of tool adoption among software engineers, and existing automated tool recommendation systems.

Researchers have explored ways humans learn about new tools. Prior work in diffusion of innovations~\cite{Rogers2003Diffusion} and persuasion theory~\cite{Shen2012Persuasion} show that the way messages are communicated impacts reception. There are a numerous methods for discovering tools in software, however, research suggests that recommendations from peers, or \textit{peer interactions}, are the most effective. Murphy-Hill found that peer interactions were the most effective mode of tool discovery among software engineers compared to chance encounters, tutorials, descriptions, social media, or discussion threads~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}. Similarly, Welty discovered that software users sought help from colleagues more than search engines and help menus~\cite{Welty2011Help}. Our work builds on the results of these studies by integrating qualities of effective peer-to-peer recommendations into an automated recommendation system.

Previous work has explored the tool adoption problem in software engineering and barriers preventing developers from adopting useful tools for important programming tasks. Researchers have created numerous tools to aid software engineers in their work, but these products are often ignored by developers~\cite{Ivanov2017Gaps}. Tilley and colleagues studied the challenges of adopting these research-of-the-shelf tools in industry~\cite{Tilley2003ROTS}. Johnson and colleagues reported reasons why software engineers don't use static analysis tools to help find and prevent bugs in their code~\cite{Johnson2013Why}. Xiao and colleagues examined barriers and social influences blocking developers from using security tools to detect and prevent vulnerabilities and malicious attacks~\cite{Xiao2014Security}. Our project aims to increase software engineer tool adoption by developing \tool~to automatically and effectively recommend useful tools to help complete development tasks.

Additionally, there are numerous existing technical approaches created to improve the tool discovery problem. Researchers have developed several active help systems using community involvement. Gordon and colleagues developed Codepourri, a system using crowdsourcing to collectively create Python tutorials~\cite{Gordon2015Codepourri}. Linton and colleagues designed a recommender system called OWL (organization-wide learning) to disseminate tool knowledge using logs throughout a company~\cite{Linton2000OWL}. ToolBox was developed as a ``community sensitive help system'' by Maltzahn to recommend Unix commands~\cite{Maltzahn1995Toolbox}. Answer Garden helps users discover new tools based on common questions asked by colleagues~\cite{Ackerman1990AnswerGarden}. SpyGlass automatically recommends tools to help users navigate code~\cite{Viriyakattiyaporn2010Spyglass}

Fischer and colleagues examined systems that require users to explicitly seek help from the software, or passive help systems~\cite{Fischer1984ActiveHelpSystems}. Fischer concluded technical passive recommendation systems, such as documentation and help menues, are ineffective and inefficient for users. Instead, active help systems are more useful for increasing tool awareness. We developed \tool~to actively suggest useful programming tools and increase awareness for software engineers. Our approach differs from existing recommendation systems in the design and implementation of our tool.

>>>>

@@

Our implementation of \tool~builds on previous research examining tool discovery, lack of tool adoption among software engineers, and automated recommendation systems.

Researchers have explored how humans learn about new tools. There are various methods to discover tools in software, and research suggests recommendations between peers is the most effective way to increase tool awareness. Murphy-Hill found that peer interactions were the most effective mode of tool discovery compared to tool encounters, tutorials, descriptions, social media, and discussion threads~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}. Similarly, Welty discovered that software users sought help from colleagues more often than search engines and help menus~\cite{Welty2011Help}. To improve the effectiveness of recommendations from our system, we integrate qualities of peer interactions into \tool.

Previous work has also explored the tool discovery problem and barriers preventing users from adopting new tools, specifically in the software engineering industry. Researchers have created numerous tools to aid software engineers in their work, but these products are often ignored by developers~\cite{Ivanov2017Gaps}. Tilley and colleagues studied the challenges of adopting these research-of-the-shelf tools in industry~\cite{Tilley2003ROTS}. Johnson and colleagues reported reasons why software engineers don't use static analysis tools to help find and prevent bugs in their code~\cite{Johnson2013Why}. Xiao and colleagues examined barriers and social influences blocking developers from using security tools to detect and prevent vulnerabilities and malicious attacks~\cite{Xiao2014Security}. Our project aims to increase tool discovery and adoption among developers by automatically recommending useful software enginering tools.

There are numerous existing technical approaches created to solve the tool discovery problem. Fischer and colleagues found that systems requiring users to explicitly seek help, or passive help systems, are ineffective and active help systems are more useful for increasing tool awareness~\cite{Fischer1984ActiveHelpSystems}. Gordon and colleagues developed Codepourri, a system using crowdsourcing to make recommendations for Python code~\cite{Gordon2015Codepourri}. Linton and colleagues designed a recommender system called OWL (organization-wide learning) to disseminate tool knowledge using logs throughout a company~\cite{Linton2000OWL}. ToolBox was developed as a ``community sensitive help system'' by Maltzahn to recommend Unix commands~\cite{Maltzahn1995Toolbox}. Answer Garden helps users discover new tools based on common questions asked by colleagues~\cite{Ackerman1990AnswerGarden}. SpyGlass automatically recommends tools to help users navigate code~\cite{Viriyakattiyaporn2010Spyglass}. We developed \tool~to actively suggest useful programming tools and increase awareness for software engineers. Our approach differs from existing recommendation systems in the design and implementation of our tool.
